Wall-to-wall mapping of peat depth from Lidar terrain and airborne radiometrics in Norwegian landscapes

### 2024-10-02 ms/ms.Rmd
ms: Orskog legacy data

>>>>

We also used two sets of existing depth measurements from Ørskogfjellet.
The first set was provided by the Norwegian Public Roads Administration, who commissioned GPR surveys of particular peatland areas in 2020 and 2021.
The surveys were conducted with a dual channel system (\unit{70\,MHz} and \unit{300\,MHz}; ImpulseRadar AB, Sweden), connected to GNSS with CPOS correction.
We used interpreted and calibrated traces from these surveys, and discarded some data where multiple depths were interpreted for the same locations.
This summed to \unit{7.4\,km} of interpreted traces.
The second set of existing depth data we extracted from a paper map made by the Norwegian Soil and Mire Company in 1984.
This map presents 44 borehole depths (in decimeters) across a \unit{9\,ha} peatland area.
We georeferenced the map and digitized the borehole locations and depths.
